### 2022-02-20 introduction/introduction.tex
new fonts

Though the interest for rigorous and formal reasoning dates back to Aristotle,
it intensified at the end of 19th and the beginning of 20th century
\cite{jf-01-modern-logic}. Researchers in that time were mostly interested in
finding a formal language that is expressive enough to describe complex
mathematical theories, yet intuitive and understandable enough to allow
reasonably simple formal reasoning systems. First-order logic seemed to satisfy
both requirements.  This formalism does not only allow one to model simple
logical relations such as ``if it rains, the road is muddy'' (or formally
$\cst{rains} \imp \cst{muddy}$), but also to quantify over objects as in ``all
people are mortal'' ($\forall x.\, \cst{human}(x) \imp \cst{mortal}(x)$).

@@

In higher-order logic we can make statements about statements. More precisely,
it treats Boolean terms (formulas) as first-class citizens, enabling us to
model some concepts in more natural manner. For example, we can naturally
represent statements such as ``what Jasmin says is true'' as $\forall x. \,
\cst{says}(\cst{jasmin}, x) \imp x$. The last stop is to support Boolean terms
as first-class citizens.
\pagebreak[2]

>>>>

Though the interest for rigorous and formal reasoning dates back to Aristotle,
it intensified at the end of 19th and the beginning of 20th century
\cite{jf-01-modern-logic}. Researchers in that time were mostly interested in
finding a formal language that is expressive enough to describe complex
mathematical theories, yet intuitive and understandable enough to allow
reasonably simple formal reasoning systems. First-order logic seemed to satisfy
both requirements.  This formalism does not only allow one to model simple
logical relations such as ``if it rains, the road is muddy'' (or formally
$\cst{rains} \imp \cst{muddy}$), but also to quantify over objects as in ``all
people are mortal'' ($\iforall x.\, \cst{human}(x) \imp \cst{mortal}(x)$).

@@

In higher-order logic we can make statements about statements. More precisely,
it treats Boolean terms (formulas) as first-class citizens, enabling us to
model some concepts in more natural manner. For example, we can naturally
represent statements such as ``what Jasmin says is true'' as $\iforall x. \,
\cst{says}(\cst{jasmin}, x) \imp x$. The last stop is to support Boolean terms
as first-class citizens.
\pagebreak[2]
